Supporting information for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2017-02-12 docs/supporting_information.tex
Fixed reference style for PNAS.
More merging...

% \usepackage[style=nature]{biblatex}
% \addbibresource{supporting_information.bib}
\usepackage[numbers, round, comma, sort&compress]{natbib}
\usepackage{hypernat}
% PNAS style: no brackets in reference list.
\makeatletter 
\renewcommand\@biblabel[1]{#1.} 
\makeatother

@@

\begin{table}
  \caption{Model parameters.}
  \label{model_param}
  \begin{tabularx}{\textwidth}{lXlll}
    \hline
    & Definition & Value & References
    \\ \hline
    $\mu$ & Background death rate
    & Country specific, Data Set 2
    & \cite{World_Development_Indicators2013-ee}
    \\
    $\kappa$ & Recruitment rate
    & Country specific, Data Set 2
    & \cite{World_Development_Indicators2013-ee, WorldBankpg}
    \\
    $\delta$ & Rate of progression from acute infection
    & $\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$
    & \cite{Hollingsworth2008-iy}
    \\
    $\sigma$ & Rate of developing AIDS without viral suppression
    & $0.1064\;\text{y$^{-1}$}$ & \cite{Morgan2002-cq}
    \\
    $\theta$ & Rate of developing AIDS with viral suppression
    & Eq.~\eqref{theta} & ---
    \\
    $\gamma$ & Rate of viral suppression
    & $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$
    & \cite{Currie2009-yz}
    \\
    $\nu$ & Death rate from AIDS & $0.5\;\text{y$^{-1}$}$
    & \cite{Morgan2002-cq}
    \\
    $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & ---
    \\
    $\omega$ & Reduction in life expectancy with viral suppression
    & $\Uniform(5, 8)\;\text{y}$
    & \cite{Samji2013-kf, Unaids2014-ue}
    \\
    $\tau_{A}$ & Transmissibility per coital act during acute phase
    & $\Triangular(0.0039, 0.0082, 0.0150)$
    & \cite{Wawer2005-us, Skarbinski2015-ni}
    \\
    $\tau_{U}$ & Transmissibility per coital act after acute phase
    & $\Triangular(0.00077, 0.0014, 0.00251)$
    & \cite{Hughes2012-so}
    \\
    $\epsilon$ & Relative transmissibility per coital act with
    viral suppression & $\BetaPERT(0.08, 0.002, 0.57)$
    & \cite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
      rodger_2016}
    \\
    $n$ & Coital acts per year & $\Uniform(96, 108)$
    & \cite{Wawer2005-us, Abdool_Karim2010-cm}
    \\
    $\alpha$ & Diagnosis rate & Eq.~\eqref{diagnosis_rate} & ---
    \\
    $\phi$ & Treatment rate & Eq.~\eqref{treatment_rate} & ---
    \\
    $\psi$ & Rate of relapse to untreated & Eq.~\eqref{relapse_rate} & ---
    \\
    $\zeta$ & Vaccination rate & Eq.~\eqref{vaccination_rate} & ---
    \\ \hline
  \end{tabularx}
  \\[5pt]
  $\Triangular$, $\Uniform$, and $\BetaPERT$ are sampling
  distributions (\autoref{uncertainty}).
  \\
  For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and $70\%$
  were also assessed in sensitivity analysis.
\end{table}

@@

The results from the country simulations were aggregated to the
regional and global levels by adding the numbers of people in each
compartment over time and then new infections, per-capita incidence,
PLHIV, and HIV-related deaths were calculated from the aggregates.
(See Data Set 6 for the definitions of UNAIDS regions.)

@@

We found sufficient published estimates and data to parametrize our
model for 127 countries.  Demographic data, including population
growth rate \cite{WorldBankpg}, death
rate \cite{World_Development_Indicators2013-ee}, and number of people
aged 15--49 years \cite{The_World_Bank2016-fd} were obtained from the
World Bank (Data Set 2). Longitudinal HIV prevalence
(Data Set 3) and incidence (Data Set 4)
estimates for ages 15--49, spanning from as early as 1990 for some
countries to 2015, were primarily obtained from the AIDSinfo database
produced by UNAIDS \cite{Unaids2016-an}. Other sources included UNAIDS
Country Progress Reports \cite{Unaids2016-am} published from 2012 to
2016 and AIDS Data Hub \cite{AIDSdatahub-fg}, which compiles data from
UNAIDS, UNICEF, WHO, and the Asian Development Bank.  These sources
were also used to inform the initial conditions for the model
regarding the number of people diagnosed with HIV, the number on ART,
and the number who have viral suppression or have been retained on
treatment for at least 12 months (Data Set 5).  Where data
or estimates were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  Full information on the sources used
for each country is provided in Data Sets 2--5.  These
source tables are also available in our public source-code
repository \cite{medlock2016-git}.

@@

We tailored our model to each of the 127 countries separately.  Using
available historical country-specific estimates of prevalence and
incidence (Data Sets 3 \& 4), and published estimates of
transmissibility per coital
act \cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
  Skarbinski2015-ni},
we derived an average country-specific transmission rate, taking into
account the differential contributions from the proportions of acute,
unsuppressed, and suppressed of the infected population in each
country.  Using historical data to smooth out short-term variations,
our calibration method provided estimates of current country-specific
transmission, as detailed below.

@@

% \printbibliography
\bibliography{supporting_information}
\bibliographystyle{pnas-new}

>>>>

\usepackage[numbers, round, comma, sort&compress]{natbib}
\usepackage{hypernat}
% PNAS style: no brackets in reference list.
\makeatletter 
\renewcommand\@biblabel[1]{#1.} 
\makeatother

@@

\begin{table}
  \caption{Model parameters.}
  \label{model_param}
  \begin{tabularx}{\textwidth}{lXlll}
    \hline
    & Definition & Value & References
    \\ \hline
    $\mu$ & Background death rate
    & Country specific, Dataset 2
    & \cite{World_Development_Indicators2013-ee}
    \\
    $\kappa$ & Recruitment rate
    & Country specific, Dataset 2
    & \cite{World_Development_Indicators2013-ee, WorldBankpg}
    \\
    $\delta$ & Rate of progression from acute infection
    & $\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$
    & \cite{Hollingsworth2008-iy}
    \\
    $\sigma$ & Rate of developing AIDS without viral suppression
    & $0.1064\;\text{y$^{-1}$}$ & \cite{Morgan2002-cq}
    \\
    $\theta$ & Rate of developing AIDS with viral suppression
    & Eq.~\eqref{theta} & ---
    \\
    $\gamma$ & Rate of viral suppression
    & $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$
    & \cite{Currie2009-yz}
    \\
    $\nu$ & Death rate from AIDS & $0.5\;\text{y$^{-1}$}$
    & \cite{Morgan2002-cq}
    \\
    $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & ---
    \\
    $\omega$ & Reduction in life expectancy with viral suppression
    & $\Uniform(5, 8)\;\text{y}$
    & \cite{Samji2013-kf, Unaids2014-ue}
    \\
    $\tau_{A}$ & Transmissibility per coital act during acute phase
    & $\Triangular(0.0039, 0.0082, 0.0150)$
    & \cite{Wawer2005-us, Skarbinski2015-ni}
    \\
    $\tau_{U}$ & Transmissibility per coital act after acute phase
    & $\Triangular(0.00077, 0.0014, 0.00251)$
    & \cite{Hughes2012-so}
    \\
    $\epsilon$ & Relative transmissibility per coital act with
    viral suppression & $\BetaPERT(0.08, 0.002, 0.57)$
    & \cite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
      rodger_2016}
    \\
    $n$ & Coital acts per year & $\Uniform(96, 108)$
    & \cite{Wawer2005-us, Abdool_Karim2010-cm}
    \\
    $\alpha$ & Diagnosis rate & Eq.~\eqref{diagnosis_rate} & ---
    \\
    $\phi$ & Treatment rate & Eq.~\eqref{treatment_rate} & ---
    \\
    $\psi$ & Rate of relapse to untreated & Eq.~\eqref{relapse_rate} & ---
    \\
    $\zeta$ & Vaccination rate & Eq.~\eqref{vaccination_rate} & ---
    \\ \hline
  \end{tabularx}
  \\[5pt]
  $\Triangular$, $\Uniform$, and $\BetaPERT$ are sampling
  distributions (\autoref{uncertainty}).
  \\
  For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and $70\%$
  were also assessed in sensitivity analysis.
\end{table}

@@

The results from the country simulations were aggregated to the
regional and global levels by adding the numbers of people in each
compartment over time and then new infections, per-capita incidence,
PLHIV, and HIV-related deaths were calculated from the aggregates.
(See Dataset 6 for the definitions of UNAIDS regions.)

@@

We found sufficient published estimates and data to parametrize our
model for 127 countries.  Demographic data, including population
growth rate \cite{WorldBankpg}, death
rate \cite{World_Development_Indicators2013-ee}, and number of people
aged 15--49 years \cite{The_World_Bank2016-fd} were obtained from the
World Bank (Dataset 2). Longitudinal HIV prevalence
(Dataset 3) and incidence (Dataset 4)
estimates for ages 15--49, spanning from as early as 1990 for some
countries to 2015, were primarily obtained from the AIDSinfo database
produced by UNAIDS \cite{Unaids2016-an}. Other sources included UNAIDS
Country Progress Reports \cite{Unaids2016-am} published from 2012 to
2016 and AIDS Data Hub \cite{AIDSdatahub-fg}, which compiles data from
UNAIDS, UNICEF, WHO, and the Asian Development Bank.  These sources
were also used to inform the initial conditions for the model
regarding the number of people diagnosed with HIV, the number on ART,
and the number who have viral suppression or have been retained on
treatment for at least 12 months (Dataset 5).  Where data
or estimates were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  Full information on the sources used
for each country is provided in Datasets 2--5.  These
source tables are also available in our public source-code
repository \cite{medlock2016-git}.

@@

We tailored our model to each of the 127 countries separately.  Using
available historical country-specific estimates of prevalence and
incidence (Datasets 3 \& 4), and published estimates of
transmissibility per coital
act \cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
  Skarbinski2015-ni},
we derived an average country-specific transmission rate, taking into
account the differential contributions from the proportions of acute,
unsuppressed, and suppressed of the infected population in each
country.  Using historical data to smooth out short-term variations,
our calibration method provided estimates of current country-specific
transmission, as detailed below.

@@

%\bibliography{\jobname}
%\bibliographystyle{pnas-jm}
% The reference list was hand editted!
\input{\jobname.bbl}
